---
title: "Cardboard Sign Experiment"
author: "Rishi"
date: "2023-12-07"
output: html_document
---

```{r setting, echo=FALSE,results= 'hide', message=FALSE }
library("dplyr")
library(greekLetters)
library(psych)
library(pwr)
```

# Sample Size Estimation 

```{r}
library(pwr)

#Since calculating the sample size for a paired proportion test requires knowing the expected proportions in each group, we will follow a conservative approximation approach which will help us ensure sufficient power. 

# Approximation - Expected change in proportion (effect size)
effect_size <- 0.5  # Assuming medium effect (0.5)

# Desired significance level and power
alpha <- 0.05
power <- 0.80

# Calculate the sample size based on the effect size
# Round up to the nearest integer because the sample size must be a whole number
sample_size <- ceiling(pwr.2p.test(h = effect_size, n = NULL, sig.level = alpha, power=0.8, alternative = "two.sided")$n)
sprintf("The sample size required to achieve power=0.8 at 5%% significance level with an assumed medium effect is %d", sample_size)
print("Since, this is just a conservative approach, we will aim for sample size higher than 63 i.e 120 for each treatment level.")
```

# First Statistical Test

# The experiment includes cardboard and gender level to understand people response

```{r}
paste(greeks("H_0"), ":There is no relationship between cardboard levels and gender.")
paste(greeks("H_1"), ":There is a relationship between cardboard levels and gender.")

# Creating the contingency table
contingency_table <- matrix(c(15, 26, 28, 30, 20, 42), nrow = 2, byrow = TRUE)
rownames(contingency_table) <- c("Male", "Female")
colnames(contingency_table) <- c("High Five", "High Five with an image", "Air High Five")

# Observed contingency table
contingency_table
# Perform chi-squared test
chi_squared_test <- chisq.test(contingency_table)
chi_squared_test

print("At 5% significance level, we have a p-value of 0.06, hence we fail to reject the null hypothesis i.e there is no significant relationship between cardboard message and gender when people respond.")
```
Since we have found out that gender doesn't play any significant role in people response to cardboard message, we will run the following test to analyze if the cardboard messages themselves differ significantly. 

# Statistical Test 2

# Description of Treatment Levels 

P1 = proportion of response with respect to the cardbord reading just "High Five"
<br>
P2 = proportion of response with respect to the cardbord reading "High Five with an image"
<br>
P3= proportion of response with respect to cardbord reading "Air High Five"
<br>
As analysed, gender doesn't play any significant role in people response with respect to these cardboard texts treatments.

```{r}
#Hypothesis
paste(greeks("H_0"), ":The proportion of people response to all cardboard treatment levels is equal i.e p1=0.33, p2=0.33, and p3=0.33")
paste(greeks("H_1"), ":Atleast one proportion differs from the expected proportion")

# response values 
response <- c(45,46,70)
# Sample sizes
sample_sizes <- c(120, 120, 120)

# Observed probability 
observed_props <- response/sample_sizes

# Expected equal proportions based on hypothesis:h0
expected_prop <- c(1/3, 1/3, 1/3)
expected_counts <- expected_prop*sample_sizes

# Calculate chi-squared statistic  
chi_squared <- sum((response - expected_counts)^2 / expected_counts)
sprintf("The chi-squared statistic value is %.3f",chi_squared)

# Degree of freedom
df <- 2 #Total 3 treatment levels 

# Calculating p-value
p_value <- 1 - pchisq(chi_squared, df)
sprintf("The p-value for the test is %.3f",p_value)

print("At 5% significance level, we can reject the null hypothesis i.e at least one of the proportion between the cardboard response is different.")
```

# Proportion Test between different pairs of cardboard text to find the most significant one

```{r}
# "High Five" vs "High Five with an image"
prop1 <- 45/120
prop2 <- 46/120
sample_size1 <- 120
sample_size2 <- 120

# Perform proportion test
prop_test <- prop.test(x = c(prop1 * sample_size1, prop2 * sample_size2),
                       n = c(sample_size1, sample_size2),
                       alternative = "two.sided")
prop_test
print("From this output, we can conlude that at 5% significance level, there is no major difference in response between cardboard that reads 'High Five' vs 'High Five with an image'")

# "High Five" vs "Air High Five"
prop1 <- 45/120
prop3 <- 70/120
sample_size1 <- 120
sample_size3 <- 120

# Perform proportion test
prop_test <- prop.test(x = c(prop1 * sample_size1, prop3 * sample_size3),
                       n = c(sample_size1, sample_size3),
                       alternative = "two.sided")
prop_test
print("From the above output, we can conlude that at 5% significance level, there is a major difference in response between cardboard that reads 'High Five' vs 'Air High Five'")

#"High Five with an image" vs "Air High Five" 
prop2 <- 46/120
prop3 <- 70/120
sample_size2 <- 120
sample_size3 <- 120

# Perform proportion test
prop_test <- prop.test(x = c(prop2 * sample_size2, prop3 * sample_size3),
                       n = c(sample_size2, sample_size3),
                       alternative = "two.sided")
prop_test
print("From the above output, we can conlude that at 5% significance level, there is a major difference in response between cardboard that reads 'High Five with an image' vs 'Air High Five'")
```

# Conclusion From First Test 

The cardboard that reads "Air High Five" has the highest proportion of response with 0.58 compared to other cardboard types, especially "High Five" which has proportion of 0.375. 
<br>
Only cardboard with "Air High Five" is statistically different from other cardboard types in terms of people response. 


